Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-09-06 paper/paper.tex
A few minor changes

\subsection{IFN reporter cell lines}
\jdbcomment{Alistair writes this}
For our type I interferon reporters, A 1kb region upstream of the human IFNB1 gene was cloned into the pHAGE2 lentiviral vector, with a NotI site immediately downstream serving as an artificial kozak sequence (REF). 
Downstream of this NotI site, each of the following reporter constructs was cloned: mCherry, mNeongreen, and mNeongreen translationally linked to LNGFR$\delta$C by a p2A linker (REFS).
For our type III interferon reporters, a 1.2kb region upstream of the human IL29 (IFNL1) gene was cloned into the pHAGE2 vector, with the native kozak sequence left at the 3' end. 
Downstream of this promoter zsGreen translationally linked to LNGFR$\delta$C via a p2A linker was cloned. 
Replication-incompetent lentivirus was generated from these vectors as previously described (REF).
A monolayer of A549 cells was transduced with each lentivirus, and sorted as single cells. 
These single cell clones were grown and tested for reporter activity by poly I:C transfection ? a potent agonist of the RIG-I pathway.
Critically, cells propagated and used in experiments were not exposed to poly I:C,  thus avoiding selection on survival post interferon-induction.
For our dual- type I and type III reporter, a single-cell clone of our type III reporter strain was transduced with our type I reporter bearing the mCherry fluorescent marker and subsequently propagated as a single cell clone and validated as above.

@@

\subsection{Viral stocks}
\jdbcomment{Alistair writes this}
All viruses were generated using reverse-genetics as previously described.
Briefly, bidirectional plasmids producing viral mRNA and vRNA are transfected into a co-culture of MDCK-SIAT1 and 293t cells grown in D10.
After 24h, media is changed from D10 to influenza growth media.
Between 48h and 72h post-infection, depending on viral growth kinetics, supernatant is harvested and titered by TCID50.
Virus is subsequently expanded on MDCK-SIAT1 cells as described below.
For all viral variants, the described mutations were introduced into reverse-genetics plasmids using PCR mutagenesis. 
For the HA-flanked mCherry pseudovirus, a plasmid was generated similarly to a previously-described HA-flanked eGFP vector.
Synonymously-barcoded virus utilized previously described 3' synonymous mutations, and two newly-introduced single-nucleotide synonymous mutations at the 5' end of each viral gene.
Wild-type, synonymously-barcoded, NS1-inactivated, and single-nucleotide variant viruses were all grown in unmodified MDCK-SIAT1 and 293t cells.
Viral variants bearing large internal deleltions in the PB1 segment were grown in MDCK-SIAT1 and 293t cells expressing PB1 as previously described.
Pseudovirus expressing mCherry in place of eGFP was grown in MDCK-SIAT1 and 293t cells expressing HA as previously described.

>>>>

\subsection{IFN reporter cell lines}
\jdbcomment{Alistair writes this}
For our type I interferon reporters, A 1kb region upstream of the human IFNB1 gene was cloned into the pHAGE2 lentiviral vector, with a NotI site immediately downstream serving as an artificial Kozak sequence (REF). 
Downstream of this NotI site, each of the following reporter constructs was cloned: mCherry, mNeongreen, and mNeongreen translationally linked to LNGFR$\delta$C by a p2A linker (REFS).
For our type III interferon reporters, a 1.2kb region upstream of the human IL29 (IFNL1) gene was cloned into the pHAGE2 vector, with the native kozak sequence left at the 3' end. 
Downstream of this promoter zsGreen translationally linked to LNGFR$\delta$C via a p2A linker was cloned. 
Replication-incompetent lentivirus was generated from these vectors as previously described (REF).
A monolayer of A549 cells in D10 was transduced with each lentivirus in the presence of 5 $\mu$g polybrene, and sorted as single cells. 
These single cell clones were grown and tested for reporter activity by poly I:C transfection---a potent agonist of the RIG-I pathway.
Critically, cells propagated and used in experiments were not exposed to poly I:C,  thus avoiding selection on survival post interferon-induction.
For our dual- type I and type III reporter, a single-cell clone of our type III reporter strain was transduced with our type I reporter bearing the mCherry fluorescent marker and subsequently propagated as a single cell clone and validated as above.

@@

\subsection{Viral stocks}
\jdbcomment{Alistair writes this}
All viruses were generated using reverse-genetics as previously described.
Briefly, bidirectional plasmids producing viral mRNA and vRNA are transfected into a co-culture of MDCK-SIAT1 and 293t cells grown in D10.
After 24h, media is changed from D10 to influenza growth media.
Between 48h and 72h post-infection, depending on viral growth kinetics, supernatant was harvested and titered by TCID50.
Virus was subsequently expanded on MDCK-SIAT1 cells as described below.
For all viral variants, the described mutations were introduced into reverse-genetics plasmids using PCR mutagenesis. 
For the HA-flanked mCherry pseudovirus, a plasmid was generated similarly to a previously-described HA-flanked eGFP vector.
Synonymously-barcoded virus utilized previously described 3' synonymous mutations, and two newly-introduced single-nucleotide synonymous mutations at the 5' end of each viral gene.
Wild-type, synonymously-barcoded, NS1-inactivated, and single-nucleotide variant viruses were all grown in unmodified MDCK-SIAT1 and 293t cells.
Viral variants bearing large internal deleltions in the PB1 segment were grown in MDCK-SIAT1 and 293t cells expressing PB1 as previously described.
Pseudovirus expressing mCherry in place of eGFP was grown in MDCK-SIAT1 and 293t cells expressing HA as previously described.
